---
title: "628 Group4 Key problem 2"
author: "Liqiang Pu"
output: html_document
---
#### Key question

#### Plan approach & Results
* 1. Combine all the data into one csv file from 2012 to 2015 for our interesting city (Here I choose Beijing).

```{r}
require(dplyr)
datacombine<-function(chr1,chr2,chr3,chr4){
  data1 <-read.csv(chr1,skip=3,colClasses = c("character",rep("NULL",2),rep("integer",5),rep("NULL",3)))
  data2 <-read.csv(chr2,skip=3,colClasses = c("character",rep("NULL",2),rep("integer",5),rep("NULL",3)))
  data3 <-read.csv(chr3,skip=3,colClasses = c("character",rep("NULL",2),rep("integer",5),rep("NULL",3)))
  data4 <-read.csv(chr4,skip=3,colClasses = c("character",rep("NULL",2),rep("integer",5),rep("NULL",3)))
  return(rbind(data1,data2,data3,data4))
}
bjdirty<-datacombine("bj2012.csv","bj2013.csv","bj2014.csv","bj2015.csv")
str(bjdirty)
```

* 2. Create a new factor variable "week" to the  dataset, set 1 as the weekday , 0 as the weekend.

```{r}
#1/1/2012 is Sunday, set variable week as 0
n<-dim(bjdirty)[1]/24 #Total days
l<-n%/%7 # Total weeks (from Mon to Sun, 7 days)
m<-n%%7-1 # here m = 4, means for 12/28/2015 to 12/31/2015 , week = 1
week<-c(rep(0,24),rep(rep(c(rep(1,5),rep(0,2)),each=24),l),rep(c(1,1,1,1),each=24))
# week variable from 1/1/2012 to 12/31/2015
bjdirty$week<-week
str(bjdirty)
```
* 3. Find all holidays (or some long-term holidays ,like spring festival) for each year, changing the corresponding week vaules.
```{r}
#Holiday informations from the Chinese Goverment website :
#2012 :http://www.gov.cn/zwgk/2011-12/06/content_2012097.htm
#2013 :http://www.gov.cn/zwgk/2012-12/10/content_2286598.htm
#2014 :http://www.gov.cn/zwgk/2013-12/11/content_2546204.htm
#2015 :http://www.gov.cn/zhengce/content/2014-12/16/content_9302.htm

#for 2012
M2012.h<-c(rep(1,10),rep(4,5),5,rep(6,3),9,rep(10,7))
D2012.h<-c(1:3,22:28,2:4,29:30,1,22:24,30,1:7)
WE2012<-paste(2012,M2012.h,D2012.h,sep="/")
M2012.w<-c(1,1,3,4,4,9)
D2012.w<-c(21,29,31,1,28,29)
WD2012<-paste(2012,M2012.w,D2012.w,sep="/")

#for 2013
M2013.h<-c(rep(1,3),rep(2,7),rep(4,5),5,rep(6,3),rep(9,3),rep(10,7))
D2013.h<-c(1:3,9:15,4:6,29:30,1,10:12,19:21,1:7)
WE2013<-paste(2013,M2013.h,D2013.h,sep="/")
M2013.w<-c(1,1,2,2,4,4,4,6,6,9,9,10)
D2013.w<-c(5,6,16,17,7,27,28,8,9,22,29,12)
WD2013<-paste(2013,M2013.w,D2013.w,sep="/")

#for 2014
M2014.h<-c(rep(1,2),rep(2,6),4,rep(5,3),6,9,rep(10,7))
D2014.h<-c(1,31,1:6,5,1:3,2,8,1:7)
WE2014<-paste(2014,M2014.h,D2014.h,sep="/")
M2014.w<-c(1,2,4,5,9,10)
D2014.w<-c(26,8,7,4,28,11)
WD2014<-paste(2014,M2014.w,D2014.w,sep="/")

#for 2015
M2015.h<-c(rep(1,3),rep(2,7),4,5,6,9,rep(10,7))
D2015.h<-c(1:3,18:24,5,20,27,1:7)
WE2015<-paste(2015,M2015.h,D2015.h,sep="/")
M2015.w<-c(1,2,2,4,6,10)
D2015.w<-c(4,15,28,6,22,10)
WD2015<-paste(2015,M2015.w,D2015.w,sep="/")

WE<-c(WE2012,WE2013,WE2014,WE2015)
WD<-c(WD2012,WD2013,WD2014,WD2015)

bjdirty<-bjdirty%>% 
mutate(date = paste(Year,Month,Day,sep="/"))
bjdirty0<-bjdirty%>%
filter(date %in% WE)%>%
mutate(week = 0)
bjdirty1<-bjdirty%>%
filter(date %in% WD)%>%
mutate(week = 1)
bjdirty2<-bjdirty%>%
filter(!date %in% c(WD,WE))

bjweek<-rbind(bjdirty0,bjdirty1,bjdirty2) %>%
arrange(Year,Month,Day)

```

* 4. Dataclean, add the pollution level accroding to the mean daily value.

```{r}
dataclean<-function(data){
    newdata<-data %>%
    filter(Value > 0) %>%
    group_by(Month,Day) %>%
    mutate(mean_Value_Day = mean(Value)) %>%
    ungroup()
    return(newdata)
}
bjclean<-dataclean(bjweek)
bjclean$DailyIndex<-as.numeric(bjclean$mean_Value_Day>=100)
bjclean$week<-gsub("0",replacement="weekend",bjclean$week)
bjclean$week<-gsub("1",replacement="weekday",bjclean$week)
bjclean$DailyIndex<-gsub("0",replacement="Light",bjclean$DailyIndex)
bjclean$DailyIndex<-gsub("1",replacement="Heavy",bjclean$DailyIndex)
knitr::kable(head(bjclean))
```

* 5. Graphical Analysis
 
```{r}
require(ggplot2)
ggplot(bjclean,aes(x=DailyIndex,group=Year,fill=week))+geom_bar(show.legend=F)+facet_grid(Year~week)+ggtitle("Heavy Vs Light in each year") 

stat<-bjclean%>%
group_by(week)%>%
summarise(sum(DailyIndex=="Heavy")/length(week),mean(Value),sd(Value))%>%
mutate(Year = "12-15")
stat1<-bjclean%>%
group_by(Year,week)%>%
summarise(sum(DailyIndex=="Heavy")/length(week),mean(Value),sd(Value))

stat_bj<-data.frame(rbind(stat1,stat))
colnames(stat_bj)<-c("Year","Week","Heavy_pollution_probability","mean_PM2.5_value","sd_PM2.5_value ")
knitr::kable(stat_bj)
ggplot(subset(stat_bj,Year!="12-15"),aes(x=Year,y=Heavy_pollution_probability,color=Week,group=Week))+geom_point()+geom_line()+ggtitle("Probability of Heavy pollution day")

ggplot(subset(stat_bj,Year!="12-15"),aes(x=Year,y=mean_PM2.5_value,color=Week,group=Week))+geom_point()+geom_line()+ggtitle("Mean PM2.5 Value")

bjclean2013_1<-bjclean %>%
filter(Year == 2013 & Month ==1 )
bjclean2015_4<-bjclean %>%
filter(Year == 2015 & Month ==4 )
bjclean2014<-bjclean %>%
filter(Year == 2014)

month_pm<-function(data){
ggplot(data,aes(x=reorder(Day,mean_Value_Day),y=mean_Value_Day,color=week))+geom_point(size=2)+geom_hline(yintercept=100,linetype="dashed") +xlab("Day")
}
month_pm(bjclean2013_1)+ ggtitle("Beijing Daily Mean Pm2.5 Values in 2013 Jan")
month_pm(bjclean2015_4)+ ggtitle("Beijing Daily Mean Pm2.5 Values in 2015 Apr")
ggplot(bjclean,aes(x=reorder(Month,mean_Value_Day),y=mean_Value_Day,color=week,group=Year))+geom_point()+geom_hline(yintercept=100,linetype="dashed") +xlab("Month")+facet_grid(~Year)+ ggtitle("Yearly Pattern for Beijing Daily Mean Pm2.5 Values")

```
