---
title: "Project1 Week 2 Report"
author: "Kejia Shi"
date: "February 4, 2016"
output: html_document
---
# Plan of Approach
Week 2 Basic exploration and analysis of the seasonal data, find possible factors and gather alternative data

Week 3 Factor analysis and time series analysis of the seasonal data

Week 4 Wrap-up

#Sources of Data
Basic dataset: StateAir (http://www.stateair.net/)

Alternative datasets and factors still in decision.


#Code for Analysis with Documentation

##0. Data Preparation

```{r, eval=FALSE}
Use pre-cleaned dataset by ditching -999 values (invalid).
setwd("/Users/KJ/OneDrive/Projects/628Air/data/")
library(dplyr)
library(ggplot2)
dataclean<-function(chr){
  data <-read.csv(chr,skip=3,colClasses = c("character",rep("NULL",2),rep("integer",5),rep("NULL",3)))
  data<-data %>%
    filter(Value != -999) %>%
    group_by(Month) %>%
    mutate(mean_Value_Mon = mean(Value)) %>%
    group_by(Month,Day) %>%
    mutate(mean_Value_Day = mean(Value)) %>%
    ungroup()
}
```

###perform first cleaning

```{r, eval=FALSE}
bj2015<-dataclean("bj2015.csv")
bj2014<-dataclean("bj2014.csv")
bj2013<-dataclean("bj2013.csv")
bj2012<-dataclean("bj2012.csv")
bj2011<-dataclean("bj2011.csv")
bj<-rbind(bj2011,bj2012,bj2013,bj2014,bj2015)
save(bj,file="bj.rdata")
```

##1. Data Cleaning: deal with negative values

```{r, eval=FALSE}
sum(bj$Value<0)
bj$Value[bj$Value<0] <- 1/2( lead(bj$Value[bj$Value<0],1,order_by = NULL) + lag(bj$Value[bj$Value<0],1,order_by = NULL) )
sum(bj$Value<0)
```

##2. Separate periods and calculate average values as daily index

Standard: from 6am to 10pm use average value of hourly data to represent daily value
Need to be fixed: Set the standard with the group of daily values
Then use daily value to completely rewrite bj dataset

##3. Separate different seasons and years and save

3/21,6/22,9/23,12/22

```{r, eval=FALSE}
Fall<-subset(bj, (bj$Month==9&bj$Day>=23)|bj$Month==10|bj$Month==11|(bj$Month==12&bj$Day<22))
Fall<-subset(Fall, Year>2011)
Fall$Season<-"Fall"
Summer<-subset(bj, (bj$Month==6&bj$Day>=22)|bj$Month==7|bj$Month==8|(bj$Month==9&bj$Day<23))
Summer<-subset(Summer, Year>2011)
Summer$Season<-"Summer"
Spring<-subset(bj, (bj$Month==3&bj$Day>=21)|bj$Month==4|bj$Month==5|(bj$Month==6&bj$Day<22))
Spring<-subset(Spring, Year>2011)
Spring$Season<-"Spring"
Winter<-subset(bj, (bj$Month==12&bj$Day>=22)|bj$Month==1|bj$Month==2|(bj$Month==3&bj$Day<21))
Winter<-subset(Winter, Year<2015)
Winter$Season<-"Winter"
bjs<-rbind(Winter,Spring,Summer,Fall)
save(Fall,file="fall.rdata")
save(Summer,file="summer.rdata")
save(Spring,file="spring.rdata")
save(Winter,file="winter.rdata")
save(bjs,file="bjs.rdata")
```

create natural year column to fix winter data

##4. First exploration of data

general inspectation

make histogram showing different season distributions in one picture

```{r, eval=FALSE}
hist(Winter$Value)
hist(Summer$Value)
ggplot(bjs, aes(Value, fill = Season)) + geom_density(alpha = 0.7)
```

do the same for each year

plot different years' data of every season

##5. Replicate for different cities
replicate for Shanghai, Chengdu

#Plan of Writeup

##Summaries and graphs
Major summary answers the following questions:

1. What are the differences between the smog patterns within different seasons?

2. What are the tendencies through 2012 to 2015?

3. What factors lead to the highs and lows in different seasons?

4. Comparisons between different cities.

This would include plots and graphs depict:

1. Distribution of the smog data

2. Time series analysis plots after possible detrend procedure

3. ...

##Proposed statement to officials

Collaborate with other team members and try to raise feasible suggestions specifically to different seasons to release the terrible air qualities.

#Estimate of Additional Time Needed to Complete Project

Two weeks
